Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated some texts

To understand how well the model fits the points—whether it fits well, works better in some positions, or fails to match the overall pattern—it is important to link and brush the points with high model error in the \pD{} error plot, \gD{} layout, and the generated model overlay on the data in \pD{}.

>>>>

To understand how well the model fits the points whether it fits well, works better in some positions, or fails to match the overall pattern. It is important to link and brush the points with high model error in the \pD{} error plot, \gD{} layout, and the generated model overlay on the data in \pD{}.
